Resonant Scattering in a Uniform Sphere with Large Optical Depth

### 2021-07-04 ms.tex
full readthrough up to discussion of xinit plots

We now compare each of the solutions for surface flux with Monte Carlo simulations. In Fig. \ref{fig:sol_mc_residual_0}, the Monte Carlo is shown with solutions $H_{\rm d}$, $H_{\rm 0}$, and $H_{\rm 0 + bc} = H_{\rm 0} + H_{\rm bc}$ over-plotted for an optical depth of $\tau_0 = 10^7$ and photons emitted at line center $\rm x_s = 0$. The solution with the correct frequency-dependent boundary condition enforced, $H_{\rm 0 + bc}$, has considerably lower residuals to Monte Carlo than the other solutions, especially in the line wing. It is evident that the divergent solution $H_{\rm d}$ fails in the line wings. The $H_{\rm bc}$ term, when added to the solution $H_0$ derived by \citet{2006ApJ...649...14D}, adequately corrects for the apparent excess of flux in the peaks of the spectrum. This peak excess is also present in previous work that used the \citet{1990ApJ...350..216N} solution, such as \citet{2015MNRAS.449.4336S} where the discrepancy is particularly noticeable for line center optical depths of $\tau_0=10^5$ and $10^6$. The boundary term resolves the slight deficit of $H_{\rm0}$ in the line wings, further improving agreement with the numerical result. Note that the residuals to the $H_0$ solution are a close match to the $H_{\rm bc}$ term, since the Monte Carlo represents the ``true'' solution, $H$, and $H_{\rm bc} = H - H_0$.

@@

 \begin{figure}
    \centering
    \includegraphics{tau_threepanel.pdf}
    \caption{Increasing the line center optical depth. Shown here are $\tau_0 = 10^5, 10^6, 10^7$ with the $x$ and $y$ axes scaled by the characteristic frequency diffusion scale $(a\tau_0)^{1/3}$. Photons are initialized with $\rm x = 0.0$.} 
    \label{fig:sol_mc_tau}
\end{figure}

Additionally, the size of the frequency-dependent boundary condition correction is dependent on the line center optical depth, which also dictates the x-position of the peak of spectrum according to Eq. \ref{eq:tau_peak_scaling}. One factor of $(a\tau_0)^{1/3}$ has been scaled out of the x-axis of Fig. \ref{fig:sol_mc_tau} such that the peaks of the distributions are vertically aligned. This scaling has also been applied to the y-axis to preserve normalization of the escape probability. From Eq. \ref{eq:hbc_scaling}, the size of the term $H_{\rm bc}$ should become smaller with larger optical depths, following a $(a\tau_0)^{-1/3}$ scaling. Indeed, agreement between $H_{0 + \rm bc}$ and the Monte Carlo points in Fig. \ref{fig:sol_mc_tau} improves as the optical depth becomes larger. At lower optical depths, the scattering of photons within the Doppler core of the line becomes important, yet our solution is not constructed to model this behavior precisely. The effects of core scattering can be seen in the Monte Carlo data, however, as the peaks of the distribution shift substantially outward in frequency from the line core for $\tau_0 = 10^5$.

>>>>

We now compare each of the previously-discussed solutions for surface flux with Monte Carlo simulations. In Fig. \ref{fig:sol_mc_residual_0}, the Monte Carlo is shown with solutions $H_{\rm d}$, $H_{\rm 0}$, and $H_{\rm 0 + bc} = H_{\rm 0} + H_{\rm bc}$ over-plotted for an optical depth of $\tau_0 = 10^7$ and photons emitted at line center $\rm x_s = 0$. The solution with the correct frequency-dependent boundary condition enforced, $H_{\rm 0 + bc}$, has considerably lower residuals to Monte Carlo than the other solutions, especially in the line wing. It is evident that the divergent solution $H_{\rm d}$ fails in the line wings. The $H_{\rm bc}$ term, when added to the solution $H_0$ derived by \citet{2006ApJ...649...14D}, adequately corrects for the apparent excess of flux in the peaks of the spectrum. This peak excess is also present in previous work that used the \citet{1990ApJ...350..216N} solution, such as \citet{2015MNRAS.449.4336S} where the discrepancy is particularly noticeable for line center optical depths of $\tau_0=10^5$ and $10^6$. The boundary term resolves the slight deficit of $H_{\rm0}$ in the line wings, further improving agreement with the numerical result. Note that the residuals to the $H_0$ solution are a close match to the $H_{\rm bc}$ term, since the Monte Carlo represents the ``true'' solution, $H$, and $H_{\rm bc} = H - H_0$.

 \begin{figure}
    \centering
    \includegraphics{tau_threepanel.pdf}
    \caption{Increasing the line center optical depth. Shown here are $\tau_0 = 10^5, 10^6, 10^7$ with the $x$ and $y$ axes scaled by the characteristic frequency diffusion scale $(a\tau_0)^{1/3}$. Photons are initialized with $\rm x = 0.0$ in each case.} 
    \label{fig:sol_mc_tau}
\end{figure}

The size of the frequency-dependent boundary condition correction is dependent on the line center optical depth, which also dictates the x-position of the peak of spectrum according to Eq. \ref{eq:tau_peak_scaling}. This term contributes a significant amount of flux correction even at line center optical depths of $10^7$ where the $J=0$ solution is expected to perform its best, i.e., the majority of photons are pushed further out into the wing and thus the simplifying assumptions made in the solution of the differential equation are better founded. One factor of $(a\tau_0)^{1/3}$ has been scaled out of the x-axis of Fig. \ref{fig:sol_mc_tau} such that the peaks of the distributions are vertically aligned. This scaling has also been applied to the y-axis to preserve normalization of the escape probability. From Eq. \ref{eq:hbc_scaling}, the size of the term $H_{\rm bc}$ should become smaller with larger optical depths, following a $(a\tau_0)^{-1/3}$ scaling. Indeed, agreement between $H_{0 + \rm bc}$ and the Monte Carlo points in Fig. \ref{fig:sol_mc_tau} improves as the optical depth becomes larger. At lower optical depths, the scattering of photons within the Doppler core of the line becomes important, yet our solution is not constructed to model this behavior precisely. The effects of core scattering can be seen in the Monte Carlo data, however, as the peaks of the distribution shift substantially outward in frequency from the line core for $\tau_0 = 10^5$.

@@
